---
title: "RDA Summary Stats"
output: html_document
date: "2024-02-13"
---

This code will be used to examine the metrics that RDA indicated were most explanatory of community similarity

## Load Libraries

```{r}
library(tidyverse)

```

## Read in and prepare data

Below are the metrics included in the RDA that were lumpde by PCA

nutrients = total nitrogen, total phosphorus, ammonia, nitrite and nitrate, and orthophosphate
elements = 
pebble size = D10, D16, D25, D50, D75, D84, D84-50, D90, IQR, Hsimpson (sediment diversity)
riparian characteristics = bank stability, riparian width, vegetative protection for right and left bank each


```{r}
chem <- read.csv("chem.f21-s22.notrib.reduced.csv")
chem.s <- filter(chem, season == "Spring") %>%
  group_by(Stream)
chem.f <- filter(chem, season == "Fall") %>%
  group_by(Stream)

hab <- read.csv("habitatmasteradj.csv") %>%
  group_by(Stream)

```

## Examine Within Stream Chemistry Gradients

# Chemistry metrics indicated by RDA in Spring

EAS: SC and Nutrients
CRO: nutrients and hardness
FRY: elements
SPC: nutrients
ROL: NPOC
LLW: hardness
All: SC, hardness, NPOC, temp, DO, nutrients

# Chemistry metrics indicated by RDA in Fall

EAS: hardness
CRO: NA
FRY: temp
SPC: NA
ROL: hardness
LLW: hardness
All: SC, hardness, elements, DO, NPOC


```{r}

chem.s.range <- chem.s %>%
  summarise(across(c("do.mgl":"so4.hco3"), ~max(.x, na.rm = TRUE)- min (.x, na.rm = TRUE)))
          
chem.f.range <- chem.f %>%
  summarise(across(c("do.mgl":"so4.hco3"), ~max(.x, na.rm = TRUE)- min (.x, na.rm = TRUE)))

write.csv(chem.s.range, "chem.s.range.csv")
write.csv(chem.f.range, "chem.f.range.csv")

```

## Examine Within Stream Habitat Gradients

Habitat metrics indicated by RDA in Spring

EAs: slope and rip.
CRO: % large cobbles
FRY: slope
SPC: wetted width
ROL: LCF
LLw: NA
ALL: % fines, slope, peb. dim., embeddedness, wetted width, rip char

Habitat metrics indicated by RDA in Fall

EAs: % fines
CRO: LCF
FRY: %fines
SPC: NA
ROL: embeddedness 
LLw: embeddedness 
ALL: wetted width, % fines, peb. dim., slope, rip. char.

```{r}
habrange <- hab %>%
  summarise(across(c("fines":"avg.slope"), ~max(.x, na.rm = TRUE)- min (.x, na.rm = TRUE)))

write.csv(habrange, "habrange.csv")
```


## 


```{r}

```


## 


```{r}

```



