---
title: "Metrics vs SC regression"
output: html_document
date: "2023-12-19"
creator: Melanie McMillan
---

## Background

In this code we  will be creating simple linear regressions for the 6 key metrics in Fall and in Spring. There will be one chart for each metric with 6 lines representing the 6 different streams. The six key metrics are as follows: Richness EPT, Richness E less B, % E, Clinger Richness, Scraper Richness, % composed of 5 most dominant taxa.

## Libraries Needed

```{r}
library(tidyverse)
library(ggpubr) #used for stat_smooth() and stat_cor

```

## Loading and Preparing the Data

You can also embed plots, for example:

```{r}
metrics <- read_csv("metrics.taxachange.csv")
metrics.s <- metrics %>%
  filter(Season == "Spring")
metrics.f <- metrics %>%
  filter(Season == "Fall")

chem <- read_csv("chem.f21-s22.notrib.reduced.csv") 
chem.s <- chem %>%
  filter(season == "Spring")
chem.f <- chem %>%
  filter(season == "Fall") %>%
  filter(Site != "SPC6")

sc <- left_join(metrics, chem, by = c("Site","Season" = "season", "Stream", "sc.uScm"))
sc$group <- factor(sc$Stream, levels = c("EAS (R)", "CRO (R)", "FRY (L)", "SPC (L)", "ROL (H)", "LLW (H)"))

sc.s <- left_join(metrics.s, chem.s, by = c("Site","Season" = "season", "Stream", "sc.uScm"))
sc.s$group <- factor(sc.s$Stream, levels = c("EAS (R)", "CRO (R)", "FRY (L)", "SPC (L)", "ROL (H)", "LLW (H)"))

sc.f <- left_join(metrics.f, chem.f, by = c("Site","Season" = "season", "Stream", "sc.uScm"))
sc.f$group <- factor(sc.f$Stream, levels = c("EAS (R)", "CRO (R)", "FRY (L)", "SPC (L)", "ROL (H)", "LLW (H)"))
```

## Plotting Spring

```{r}
pE.s<- sc.s %>% ggplot(aes(x=sc.uScm , y=pE))+
  geom_point(aes(color = group, shape = group))  +
  geom_smooth(method = "lm", linetype = 2) +
  stat_cor(method = "spearman", label.x = 1000, show.legend = FALSE) +
  theme_classic()+
  scale_colour_manual(name = "Impact Level and Stream",
                      values = c("#619CFF", "#619CFF", "#00BA38", "#00BA38","#F8766D", "#F8766D"),
                      labels = c("R1","R2","L1", "L2","H1","H2")) +
  scale_shape_manual(name = "Impact Level and Stream",
                     values = c(1, 16, 0, 15, 2, 17), labels = c("R1","R2","L1", "L2","H1","H2"))+
  xlab("SC (uS/cm)") +
  ylab("% E") 
pE.s

richsc.s<- sc.s %>% ggplot(aes(x=sc.uScm , y=rich.SC, color = group, shape = group))+
  geom_point()  +
  stat_smooth(method = "lm", linetype = 2) +
  stat_cor(method = "spearman", label.x = 1000, show.legend = FALSE) +
  theme_classic()+
  scale_colour_manual(name = "Impact Level and Stream",
                      values = c("#619CFF", "#619CFF", "#00BA38", "#00BA38","#F8766D", "#F8766D")) +
  scale_shape_manual(name = "Impact Level and Stream",
                     values = c(1, 16, 0, 15, 2, 17))+
  xlab("SC (uS/cm)") +
  ylab("Scraper Richness") 
richsc.s

rich.EPT.s<- sc.s %>% ggplot(aes(x=sc.uScm , y=rich.EPT, color = group, shape = group))+
  geom_point()  +
  stat_smooth(method = "lm", linetype = 2) +
  stat_cor(method = "spearman", label.x = 1000, show.legend = FALSE) +
  theme_classic()+
  scale_colour_manual(name = "Impact Level and Stream",
                      values = c("#619CFF", "#619CFF", "#00BA38", "#00BA38","#F8766D", "#F8766D")) +
  scale_shape_manual(name = "Impact Level and Stream",
                     values = c(1, 16, 0, 15, 2, 17))+
  xlab("SC (uS/cm)") +
  ylab("Richness EPT") 
rich.EPT.s

richelessb.s<- sc.s %>% ggplot(aes(x=sc.uScm , y=rich.E.less.B, color = group, shape = group))+
  geom_point()  +
  stat_smooth(method = "lm", linetype = 2) +
  stat_cor(method = "spearman", label.x = 1000, show.legend = FALSE) +
  theme_classic()+
  scale_colour_manual(name = "Impact Level and Stream",
                      values = c("#619CFF", "#619CFF", "#00BA38", "#00BA38","#F8766D", "#F8766D")) +
  scale_shape_manual(name = "Impact Level and Stream",
                     values = c(1, 16, 0, 15, 2, 17))+
  xlab("SC (uS/cm)") +
  ylab("Richness E less B") 
richelessb.s

richcling.s<- sc.s %>% ggplot(aes(x=sc.uScm , y=rich.Cling, color = group, shape = group))+
  geom_point()  +
  stat_smooth(method = "lm", linetype = 2) +
  stat_cor(method = "spearman", label.x = 1000, show.legend = FALSE) +
  theme_classic()+
  scale_colour_manual(name = "Impact Level and Stream",
                      values = c("#619CFF", "#619CFF", "#00BA38", "#00BA38","#F8766D", "#F8766D")) +
  scale_shape_manual(name = "Impact Level and Stream",
                     values = c(1, 16, 0, 15, 2, 17))+
  xlab("SC (uS/cm)") +
  ylab("Clinger Richness") 
richcling.s

p5dom.s<- sc.s %>% ggplot(aes(x=sc.uScm , y=p5dom, color = group, shape = group))+
  geom_point()  +
  stat_smooth(method = "lm", linetype = 2) +
  stat_cor(method = "spearman", label.y = c(85, 82, 79, 76, 73, 70), label.x= 1000, show.legend = FALSE) +
  theme_classic()+
  scale_colour_manual(name = "Impact Level and Stream",
                      values = c("#619CFF", "#619CFF", "#00BA38", "#00BA38","#F8766D", "#F8766D")) +
  scale_shape_manual(name = "Impact Level and Stream",
                     values = c(1, 16, 0, 15, 2, 17))+
  xlab("SC (uS/cm)") +
  ylab("% 5 Dominant") 
p5dom.s

vsci.s<- sc.s %>% ggplot(aes(x=sc.uScm , y=vsci, color = group, shape = group))+
  geom_point()  +
  stat_smooth(method = "lm", linetype = 2) +
  stat_cor(method = "spearman", label.y = c(85, 82, 79, 76, 73, 70), label.x= 1000, show.legend = FALSE) +
  theme_classic()+
  scale_colour_manual(name = "Impact Level and Stream",
                      values = c("#619CFF", "#619CFF", "#00BA38", "#00BA38","#F8766D", "#F8766D")) +
  scale_shape_manual(name = "Impact Level and Stream",
                     values = c(1, 16, 0, 15, 2, 17))+
  xlab("SC (uS/cm)") +
  ylab("VSCI") 
vsci.s

corr.metrics.sc.s <- ggarrange(rich.EPT.s, richelessb.s, pE.s, richcling.s, richsc.s, p5dom.s, nrow = 3, ncol=2,  
                  common.legend = TRUE, legend = "right")
corr.metrics.sc.s
```

## Plotting Fall

```{r}
pE.f<- sc.f %>% ggplot(aes(x=sc.uScm , y=pE, color = group, shape = group, linetype = season))+
  geom_point()  +
  stat_smooth(method = "lm") +
  stat_cor(method = "spearman", label.x = 1000, show.legend = FALSE) +
  theme_classic()+
  scale_colour_manual(name = "Impact Level and Stream",
                      values = c("#619CFF", "#619CFF", "#00BA38", "#00BA38","#F8766D", "#F8766D")) +
  scale_shape_manual(name = "Impact Level and Stream",
                     values = c(1, 16, 0, 15, 2, 17))+
  xlab("SC (uS/cm)") +
  ylab("% E") 
pE.f

richsc.f<- sc.f %>% ggplot(aes(x=sc.uScm , y=rich.SC, color = group, shape = group))+
  geom_point()  +
  stat_smooth(method = "lm", linetype = 2) +
  stat_cor(method = "spearman", label.x = 1000, show.legend = FALSE) +
  theme_classic()+
  scale_colour_manual(name = "Impact Level and Stream",
                      values = c("#619CFF", "#619CFF", "#00BA38", "#00BA38","#F8766D", "#F8766D")) +
  scale_shape_manual(name = "Impact Level and Stream",
                     values = c(1, 16, 0, 15, 2, 17))+
  xlab("SC (uS/cm)") +
  ylab("Scraper Richness") 
richsc.f

rich.EPT.f<- sc.f %>% ggplot(aes(x=sc.uScm , y=rich.EPT, color = group, shape = group))+
  geom_point()  +
  stat_smooth(method = "lm", linetype = 2) +
  stat_cor(method = "spearman", label.x = 1000, show.legend = FALSE) +
  theme_classic()+
  scale_colour_manual(name = "Impact Level and Stream",
                      values = c("#619CFF", "#619CFF", "#00BA38", "#00BA38","#F8766D", "#F8766D")) +
  scale_shape_manual(name = "Impact Level and Stream",
                     values = c(1, 16, 0, 15, 2, 17))+
  xlab("SC (uS/cm)") +
  ylab("Richness EPT") 
rich.EPT.f

richelessb.f<- sc.f %>% ggplot(aes(x=sc.uScm , y=rich.E.less.B, color = group, shape = group))+
  geom_point()  +
  stat_smooth(method = "lm", linetype = 2) +
  stat_cor(method = "spearman", label.x = 1000, show.legend = FALSE) +
  theme_classic()+
  scale_colour_manual(name = "Impact Level and Stream",
                      values = c("#619CFF", "#619CFF", "#00BA38", "#00BA38","#F8766D", "#F8766D")) +
  scale_shape_manual(name = "Impact Level and Stream",
                     values = c(1, 16, 0, 15, 2, 17))+
  xlab("SC (uS/cm)") +
  ylab("Richness E less B") 
richelessb.f

richcling.f<- sc.f %>% ggplot(aes(x=sc.uScm , y=rich.Cling, color = group, shape = group))+
  geom_point()  +
  stat_smooth(method = "lm", linetype = 2) +
  stat_cor(method = "spearman", label.x = 1000, show.legend = FALSE) +
  theme_classic()+
  scale_colour_manual(name = "Impact Level and Stream",
                      values = c("#619CFF", "#619CFF", "#00BA38", "#00BA38","#F8766D", "#F8766D")) +
  scale_shape_manual(name = "Impact Level and Stream",
                     values = c(1, 16, 0, 15, 2, 17))+
  xlab("SC (uS/cm)") +
  ylab("Clinger Richness") 
richcling.f

p5dom.f<- sc.f %>% ggplot(aes(x=sc.uScm , y=p5dom, color = group, shape = group))+
  geom_point()  +
  stat_smooth(method = "lm", linetype = 2) +
  stat_cor(method = "spearman", label.x = 1000, show.legend = FALSE) +
  theme_classic()+
  scale_colour_manual(name = "Impact Level and Stream",
                      values = c("#619CFF", "#619CFF", "#00BA38", "#00BA38","#F8766D", "#F8766D")) +
  scale_shape_manual(name = "Impact Level and Stream",
                     values = c(1, 16, 0, 15, 2, 17))+
  xlab("SC (uS/cm)") +
  ylab("% 5 Dominant") 
p5dom.f

vsci.f<- sc.f %>% ggplot(aes(x=sc.uScm , y=vsci, color = group, shape = group))+
  geom_point()  +
  stat_smooth(method = "lm", linetype = 2) +
  stat_cor(method = "spearman", label.x = 1000, show.legend = FALSE) +
  theme_classic()+
  scale_colour_manual(name = "Impact Level and Stream",
                      values = c("#619CFF", "#619CFF", "#00BA38", "#00BA38","#F8766D", "#F8766D")) +
  scale_shape_manual(name = "Impact Level and Stream",
                     values = c(1, 16, 0, 15, 2, 17))+
  xlab("SC (uS/cm)") +
  ylab("VSCI") 
vsci.f

corr.metrics.sc.f <- ggarrange(rich.EPT.f, richelessb.f, pE.f, richcling.f, richsc.f, p5dom.f, vsci.f, nrow = 4, ncol=2,  
                  common.legend = TRUE, legend = "right")
corr.metrics.sc.f
```


## Plotting both seasons togehter


```{r}
pE<- sc %>% ggplot(aes(x=sc.uScm , y=pE, group = Season, shape = group, color = group, linetype = Season))+
  geom_point(size = 4)  +
  stat_smooth(method = "lm") +
  stat_cor(method = "spearman", label.x = 750, show.legend = FALSE, size = 5) +
  scale_colour_discrete(name = "Stream (Impact Level)") +
   scale_colour_manual(name = "Impact Level and Stream",
                      values = c("#619CFF", "#619CFF", "#00BA38", "#00BA38","#F8766D", "#F8766D"), labels = c("R1","R2","L1", "L2","H1","H2")) +
  scale_shape_manual(name = "Impact Level and Stream",
                     values = c(1, 16, 0, 15, 2, 17), labels = c("R1","R2","L1", "L2","H1","H2"))+
  theme_classic()+
  xlab("SC (uS/cm)") +
  ylab("% E") +
   theme( axis.title.x =element_text(size = 15), axis.text.x = element_text(size = 15),
        axis.title.y =element_text(size = 15), axis.text.y  = element_text(size = 15),
        strip.text.x = element_text(size = 15), 
        legend.text=element_text(size=15), legend.title=element_text(size=15)) 
pE

richsc <- sc %>% ggplot(aes(x=sc.uScm , y=rich.SC,  group = Season, shape = group, color = group, linetype = Season))+
  geom_point(size = 4)  +
  stat_smooth(method = "lm") +
  stat_cor(method = "spearman", label.x = 750, show.legend = FALSE, size = 5) +
  scale_colour_discrete(name = "Stream (Impact Level)") +
   scale_colour_manual(name = "Impact Level and Stream",
                      values = c("#619CFF", "#619CFF", "#00BA38", "#00BA38","#F8766D", "#F8766D"), labels = c("R1","R2","L1", "L2","H1","H2")) +
  scale_shape_manual(name = "Impact Level and Stream",
                     values = c(1, 16, 0, 15, 2, 17), labels = c("R1","R2","L1", "L2","H1","H2"))+
  theme_classic()+
  xlab("SC (uS/cm)") +
  ylab("Scraper Richness") +
   theme( axis.title.x =element_text(size = 15), axis.text.x = element_text(size = 15),
        axis.title.y =element_text(size = 15), axis.text.y  = element_text(size = 15),
        strip.text.x = element_text(size = 15), 
        legend.text=element_text(size=15), legend.title=element_text(size=15)) 
richsc

rich.EPT<- sc %>% ggplot(aes(x=sc.uScm , y=rich.EPT,  group = Season, shape = group, color = group, linetype = Season))+
  geom_point(size = 4)  +
  stat_smooth(method = "lm") +
  stat_cor(method = "spearman", label.x = 750, show.legend = FALSE, size = 5) +
  scale_colour_discrete(name = "Stream (Impact Level)") +
   scale_colour_manual(name = "Impact Level and Stream",
                      values = c("#619CFF", "#619CFF", "#00BA38", "#00BA38","#F8766D", "#F8766D"), labels = c("R1","R2","L1", "L2","H1","H2")) +
  scale_shape_manual(name = "Impact Level and Stream",
                     values = c(1, 16, 0, 15, 2, 17), labels = c("R1","R2","L1", "L2","H1","H2"))+
  theme_classic()+
  xlab("SC (uS/cm)") +
  ylab("Richness EPT") +
   theme( axis.title.x =element_text(size = 15), axis.text.x = element_text(size = 15),
        axis.title.y =element_text(size = 15), axis.text.y  = element_text(size = 15),
        strip.text.x = element_text(size = 15), 
        legend.text=element_text(size=15), legend.title=element_text(size=15)) 
rich.EPT

richelessb<- sc %>% ggplot(aes(x=sc.uScm , y=rich.E.less.B,  group = Season, shape = group, color = group, linetype = Season))+
  geom_point(size = 4)  +
  stat_smooth(method = "lm") +
  stat_cor(method = "spearman", label.x = 750, show.legend = FALSE, size = 5) +
  scale_colour_discrete(name = "Stream (Impact Level)") +
   scale_colour_manual(name = "Impact Level and Stream",
                      values = c("#619CFF", "#619CFF", "#00BA38", "#00BA38","#F8766D", "#F8766D"), labels = c("R1","R2","L1", "L2","H1","H2")) +
  scale_shape_manual(name = "Impact Level and Stream",
                     values = c(1, 16, 0, 15, 2, 17), labels = c("R1","R2","L1", "L2","H1","H2"))+
  theme_classic()+
  xlab("SC (uS/cm)") +
  ylab("Richness E less B") +
   theme( axis.title.x =element_text(size = 15), axis.text.x = element_text(size = 15),
        axis.title.y =element_text(size = 15), axis.text.y  = element_text(size = 15),
        strip.text.x = element_text(size = 15), 
        legend.text=element_text(size=15), legend.title=element_text(size=15)) 
richelessb

richcling<- sc %>% ggplot(aes(x=sc.uScm , y=rich.Cling,  group = Season, shape = group, color = group, linetype = Season))+
  geom_point(size = 4)  +
  stat_smooth(method = "lm") +
  stat_cor(method = "spearman", label.x = 750, show.legend = FALSE, size = 5) +
  scale_colour_discrete(name = "Stream (Impact Level)") +
   scale_colour_manual(name = "Impact Level and Stream",
                      values = c("#619CFF", "#619CFF", "#00BA38", "#00BA38","#F8766D", "#F8766D"), labels = c("R1","R2","L1", "L2","H1","H2")) +
  scale_shape_manual(name = "Impact Level and Stream",
                     values = c(1, 16, 0, 15, 2, 17), labels = c("R1","R2","L1", "L2","H1","H2"))+
  theme_classic()+
  xlab("SC (uS/cm)") +
  ylab("Clinger Richness") +
   theme( axis.title.x =element_text(size = 15), axis.text.x = element_text(size = 15),
        axis.title.y =element_text(size = 15), axis.text.y  = element_text(size = 15),
        strip.text.x = element_text(size = 15), 
        legend.text=element_text(size=15), legend.title=element_text(size=15)) 
richcling

p5dom <- sc %>% ggplot(aes(x=sc.uScm , y=p5dom,  group = Season, shape = group, color = group, linetype = Season))+
  geom_point(size = 4)  +
  stat_smooth(method = "lm") +
  stat_cor(method = "spearman", label.x = 750, show.legend = FALSE, size = 5) +
  scale_colour_discrete(name = "Stream (Impact Level)") +
   scale_colour_manual(name = "Impact Level and Stream",
                      values = c("#619CFF", "#619CFF", "#00BA38", "#00BA38","#F8766D", "#F8766D"), labels = c("R1","R2","L1", "L2","H1","H2")) +
  scale_shape_manual(name = "Impact Level and Stream",
                     values = c(1, 16, 0, 15, 2, 17), labels = c("R1","R2","L1", "L2","H1","H2"))+
  theme_classic()+
  xlab("SC (uS/cm)") +
  ylab("% 5 Dominant") +
   theme( axis.title.x =element_text(size = 15), axis.text.x = element_text(size = 15),
        axis.title.y =element_text(size = 15), axis.text.y  = element_text(size = 15),
        strip.text.x = element_text(size = 15), 
        legend.text=element_text(size=15), legend.title=element_text(size=15)) 
p5dom

vsci <- sc %>% ggplot(aes(x=sc.uScm , y=vsci,  group = Season, shape = group, color = group, linetype = Season))+
  geom_point(size = 4)  +
  stat_smooth(method = "lm") +
  stat_cor(method = "spearman", label.x = 750, show.legend = FALSE, size = 5) +
  scale_colour_discrete(name = "Stream (Impact Level)") +
   scale_colour_manual(name = "Impact Level and Stream",
                      values = c("#619CFF", "#619CFF", "#00BA38", "#00BA38","#F8766D", "#F8766D"), labels = c("R1","R2","L1", "L2","H1","H2")) +
  scale_shape_manual(name = "Impact Level and Stream",
                     values = c(1, 16, 0, 15, 2, 17), labels = c("R1","R2","L1", "L2","H1","H2"))+
  theme_classic()+
  xlab("SC (uS/cm)") +
  ylab("VSCI") +
   theme( axis.title.x =element_text(size = 15), axis.text.x = element_text(size = 15),
        axis.title.y =element_text(size = 15), axis.text.y  = element_text(size = 15),
        strip.text.x = element_text(size = 15), 
        legend.text=element_text(size=15), legend.title=element_text(size=15)) 
vsci 

corr.metrics.sc <- ggarrange(rich.EPT, richelessb, pE, richcling, richsc, p5dom, vsci, nrow = 4, ncol=2,  
                  common.legend = TRUE, legend = "right")
corr.metrics.sc

png("corr.metrics.sc.png", width= 800, height = 1000)
plot(corr.metrics.sc)
dev.off()

```
