---
title: "Similarity_Plots"
output: html_document
date: "2023-12-29"
author: Melanie McMillan
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Background

In this code we  will be creating simple linear regressions for Bray-Curtis Similarity values within each stream to distance between samples and then to SC

##Libraries needed

```{r}
library(tidyverse)
library(ggpubr)
```

## Prepare data


```{r}
Similar <- read_csv("Similarity.taxachange.csv")
Similar$group <- factor(Similar$Stream, levels = c("EAS (R)", "CRO (R)", "FRY (L)", "SPC (L)", "ROL (H)", "LLW (H)"))

Similar.s <- read_csv("Similarity.taxachange.csv") %>%
  filter(Season == "Spring")
Similar.s$group <- factor(Similar.s$Stream, levels = c("EAS (R)", "CRO (R)", "FRY (L)", "SPC (L)", "ROL (H)", "LLW (H)"))

Similar.f <- read_csv("Similarity.taxachange.csv") %>%
  filter(Season == "Fall")
Similar.f$group <- factor(Similar.f$Stream, levels = c("EAS (R)", "CRO (R)", "FRY (L)", "SPC (L)", "ROL (H)", "LLW (H)"))
```

##Create a Spring and fall Plot for Similarity vs Distance Between Samples


```{r}
sim.dis.s <- Similar.s %>% ggplot(aes(x=dis.simm , y=SIM.b, color = group, shape = group))+
  geom_point()  +
  facet_wrap("group", nrow = 3) +
  stat_smooth(method = "lm", linetype = 2) +
  stat_cor(method = "spearman", label.x = 0, label.y = 1) +
 scale_colour_manual(name = "Impact Level and Stream",
                      values = c("#619CFF", "#619CFF", "#00BA38", "#00BA38","#F8766D", "#F8766D")) +
  scale_shape_manual(name = "Impact Level and Stream",
                     values = c(1, 16, 0, 15, 2, 17))+
  theme_classic()+
  xlab("Distance Between Samples (m)") + # (uS/cm)
  ylab("Bray-Curtis Similarity") 

sim.dis.s 

sim.dis.f <- Similar.f %>% ggplot(aes(x=dis.simm , y=SIM.b, color = group, shape = group))+
  geom_point()  +
  facet_wrap("group", nrow = 3) +
  stat_smooth(method = "lm", linetype = 2) +
  stat_cor(method = "spearman", label.x = 0, label.y = 1) +
 scale_colour_manual(name = "Impact Level and Stream",
                      values = c("#619CFF", "#619CFF", "#00BA38", "#00BA38","#F8766D", "#F8766D")) +
  scale_shape_manual(name = "Impact Level and Stream",
                     values = c(1, 16, 0, 15, 2, 17))+
  theme_classic()+
  xlab("Distance Between Samples (m)") + # (uS/cm)
  ylab("Bray-Curtis Similarity") 

sim.dis.f
```
##Create a Spring and fall Plot for Similarity vs Change in SC Between Samples


```{r}
sim.sc.s <- Similar.s %>% ggplot(aes(x=sc.delt , y=SIM.b, color = group, shape = group))+
  geom_point()  +
  facet_wrap("group", nrow = 3) +
  stat_smooth(method = "lm", linetype = 2) +
  stat_cor(method = "spearman", label.x = 0, label.y = 1) +
 scale_colour_manual(name = "Impact Level and Stream",
                      values = c("#619CFF", "#619CFF", "#00BA38", "#00BA38","#F8766D", "#F8766D")) +
  scale_shape_manual(name = "Impact Level and Stream",
                     values = c(1, 16, 0, 15, 2, 17))+
  theme_classic()+
  xlab("Change in SC (uS/cm) Between Samples") + 
  ylab("Bray-Curtis Similarity") 

sim.sc.s 

sim.sc.f <- Similar.f %>% ggplot(aes(x=sc.delt , y=SIM.b, color = group, shape = group))+
  geom_point()  +
  facet_wrap("group", nrow = 3) +
  stat_smooth(method = "lm", linetype = 2) +
  stat_cor(method = "spearman", label.x = 0, label.y = 1) +
 scale_colour_manual(name = "Impact Level and Stream",
                      values = c("#619CFF", "#619CFF", "#00BA38", "#00BA38","#F8766D", "#F8766D")) +
  scale_shape_manual(name = "Impact Level and Stream",
                     values = c(1, 16, 0, 15, 2, 17))+
  theme_classic()+
  xlab("Change in SC (uS/cm) Between Samples") + 
  ylab("Bray-Curtis Similarity") 

sim.sc.f
```

## Plot Similarity versus sc and distance between samples for fall and spring together faceted by stream


```{r}
stream_names <- list('EAS (R)' = "R1",
  "CRO (R)" = "R2",
  "FRY (L)" = "L1",
  "SPC (L)" = "L2",
  "ROL (H)" = "H1",
  "LLW (H)" = "H2" )
stream_labeller <- function(variable,value){
  return(stream_names[value])
}

sim.sc <- Similar %>% ggplot(aes(x=sc.delt , y=SIM.b, shape = group, color = group, group = Season, linetype = Season))+
  geom_point(size = 2)  +
  facet_wrap(. ~ group, labeller = stream_labeller) +
  stat_smooth(method = "lm") +
  stat_cor(method = "spearman",label.y.npc = 0.2, size = 5) +
 scale_colour_manual(name = "Impact Level and Stream",
                      values = c("#619CFF", "#619CFF", "#00BA38", "#00BA38","#F8766D", "#F8766D"),
                     labels = c("R1","R2","L1", "L2","H1","H2")) +
   scale_shape_manual(name = "Impact Level and Stream",
                     values = c(1, 16, 0, 15, 2, 17), labels = c("R1","R2","L1", "L2","H1","H2"))+
  theme_classic()+
  xlab("Change in SC (uS/cm) Between Samples") + 
  ylab("Bray-Curtis Similarity") +
   theme( axis.title.x =element_text(size = 15), axis.text.x = element_text(size = 15),
        axis.title.y =element_text(size = 15), axis.text.y  = element_text(size = 15),
        strip.text.x = element_text(size = 15), 
        legend.text=element_text(size=15), legend.title=element_text(size=15)) 

sim.sc 

png("sim.sc .png",  width= 700, height = 600)
plot(sim.sc)
dev.off()

sim.dis <- Similar %>% ggplot(aes(x=dis.simm , y=SIM.b, shape = group, color = group, group = Season, linetype = Season))+
  geom_point(size = 2)  +
  facet_wrap(. ~ group, labeller = stream_labeller) +
  stat_smooth(method = "lm") +
  stat_cor(method = "spearman",label.y.npc = 0.2, size = 5) +
  scale_shape_manual(name = "Impact Level and Stream", 
                      values = c(1, 16, 0, 15, 2, 17), 
                      labels = c("R1","R2","L1", "L2","H1","H2"))+
  scale_colour_manual(name = "Impact Level and Stream",
                      values = c("#619CFF", "#619CFF", "#00BA38", "#00BA38","#F8766D", "#F8766D"),
                     labels = c("R1","R2","L1", "L2","H1","H2")) +
  theme_classic()+
  xlab("Distance Between Samples (m)") +
  ylab("Bray-Curtis Similarity") +
   theme( axis.title.x =element_text(size = 15), axis.text.x = element_text(size = 15),
        axis.title.y =element_text(size = 15), axis.text.y  = element_text(size = 15),
        strip.text.x = element_text(size = 15), 
        legend.text=element_text(size=15), legend.title=element_text(size=15)) 

sim.dis

png("sim.dis.png", width= 700, height = 600)
plot(sim.dis)
dev.off()
```